---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# hexwall

The `hexwall.R` file contains one function `hexwall()`, which can be used to generate an image that neatly arranges a folder of hexagons. It makes use of the [ImageMagick](https://www.imagemagick.org/) library via the ROpenSci package [magick](https://github.com/ropensci/magick) to arrange the images.

There are several arguments allowing some control over the function's operation.

* path:             The path to a folder of hexagon stickers (png files are recommended)
* sticker_row_size: The number of stickers in the longest row
* sticker_width:    The width of each sticker in pixels
* remove_small:     Should hexagons smaller than the sticker_width be removed?
* remove_size:      Should hexagons of an abnormal size be removed?
* coords:           A data.frame of coordinates defining the placement of hexagons
* scale_coords:     Should the coordinates be scaled to the hexagon size?
* sort_mode:        How should the files be sorted?

```{r example}
source("hexwall.R")
hexwall("samplehex", sticker_row_size = 3, sticker_width = 200)
```

# Usage

1. [Download the repository](https://github.com/mitchelloharawild/hexwall/archive/master.zip)
2. Unzip and open the R project (`hexwall.Rproj`)
3. Run `source("hexwall.R")`
4. Ready to go, use the `hexwall()` function to make your hexagon wall.